Risk Perceptions for Wearable Devices

### 2015-03-05 tex-inputs/results-openended.tex
made it so every tex input file can compile the paper
reworded things in open-ended section

\subsection{Self-Reported Concerns for Wearables}
We also wanted to capture the participants' general reactions to wearable devices as a whole. To do this, we asked the participants the following open-ended question:

@@

This question was asked along with demographics questions (but before any IUIPC questions to avoid biasing). The participants were presented with a blank box to write in, with no character limit to their open-ended responses. \\

Without a doubt, the most common self-reported concern of wearables for the average user is the \textit{possible loss of privacy} (see Table \ref{openresponses}). Other significant concerns included being unaware of what the device is collecting, doing, or which information it is using (Being Unaware), long-term health effects caused from wearing the device such as cancer from emf waves (Health), safety hazards from wearing the device such as distractions which cause car accidents (Safety), resulting changes in social behaviors, such as dependencies on devices or spending less time with loved ones (Social Impact), the high financial cost of buying, replacing, or caring for the device (Financial), and information compromise (Security).

>>>>

%!TEX root = ../paper.tex
\subsection{Self-Reported Concerns for Wearables}
We also wanted to capture the participants' general reactions to wearable devices as a whole. To do this, we asked the participants the following open-ended question:

@@

This question was asked along with demographics questions (but before any IUIPC questions to avoid biasing). The participants were presented with a blank box to write in, with no character limit to their open-ended responses.

 Table \ref{openresponses} shows the most common user concerns related to wearable devices. Appendix \ref{sec:coding} details the responses categorized in each coding label. Most of these concerns are related to privacy and security, but this self-report gives a sense of what broad categories of concerns are most relevant to users. This can be used to guide research in unexplored use cases.

In addition to privacy in a general sense, significant concerns included being unaware of what the device is collecting, doing, or which information it is using (Being Unaware), long-term health effects caused from wearing the device such as cancer from emf waves (Health), safety hazards from wearing the device, such as distractions which cause car accidents (Safety), resulting changes in social behaviors, such as dependencies on devices or spending less time with loved ones (Social Impact), the high financial cost of buying, replacing, or caring for the device (Financial), and information compromise (Security).

### 2015-03-05 tex-inputs/results-recipient.tex
initial progress on results:devices
reworded things in open-ended section

\subsubsection{Data Recipient}
Across all scenarios, 42.3\% of participants stated that they would be ``very upset'' if their data was shared with only the app's servers, whereas the VURs for friends (69.5\%), work contacts (75.2\%), and the public (72.4\%) were much higher. A chi-square test indicated that these differences were statistically significant (Table \ref{recipient}). However, these effect sizes were small: the largest effect was between work contacts and an app's server ($\phi=0.11$); while the VUR for sharing with work contacts was significantly higher than sharing with friends, the effect size was negligible ($\phi=0.004$).

@@

\begin{table}[t]
\begin{center}
\small
\begin{tabular}{| r | l | r | l |c |}
\hline
Rank & Recipient & VUR & sigma & Distribution \\
\hline
1 & Work Contacts & 75.16\% & 0.94 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/recipient4/recipient_work} \\
2 & Public & 72.41\% & 0.98 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/recipient4/recipient_pub}  \\
3 & Friends & 69.47\% & 1.02 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/recipient4/recipient_friends}\\
4 & App's Server & 42.28\% & 1.15 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/recipient4/recipient_app}\\
\hline
\end{tabular}
\caption{The overall upset rate for all recipients.}
\label{recipient-table}
\end{center}
\end{table}

>>>>

\subsubsection{Data Recipient}
Across all scenarios, 42\% of participants stated that they would be ``very upset'' if their data was shared with only the app's servers, whereas the VURs for friends (70\%), work contacts (75\%), and the public (72\%) were much higher (Table \ref{recipient-vur}). A chi-square test indicated that these differences were statistically significant (Table \ref{recipient-chi}). However, these effect sizes were small: the largest effect was between work contacts and an app's server ($\phi=0.11$); while the VUR for sharing with work contacts was significantly higher than sharing with friends, the effect size was negligible ($\phi=0.004$).

@@

\begin{table}[t]
\begin{center}
\small
\begin{tabular}{| r | l | r | l |c |}
\hline
Rank & Recipient & VUR & sigma & Distribution \\
\hline
1 & Work Contacts & 75.16\% & 0.94 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/recipient4/recipient_work} \\
2 & Public & 72.41\% & 0.98 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/recipient4/recipient_pub}  \\
3 & Friends & 69.47\% & 1.02 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/recipient4/recipient_friends}\\
4 & App's Server & 42.28\% & 1.15 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/recipient4/recipient_app}\\
\hline
\end{tabular}
\caption{The overall upset rate for all recipients.}
\label{recipient-vur}
\end{center}
\end{table}

\begin{table}[t]
\begin{center}
\begin{tabular}{|l|r|r|r|r|}
\hline
Recipients	& $\chi^2$ & p-value 	& n & $\phi$ \\
\hline
Work-App	& 565.910 & <0.0001 & 5,083 & 0.111\\
Public-App	& 481.776 & <0.0001 & 5,1988& 0.093\\
Friends-App & 381.653 & <0.0001 & 5,096 & 0.075\\
Friends-Work & 20.39 & <0.0001 & 5,037 & 0.004\\
Friends-Public & 5.41 & <0.0200 & 5,142 & 0.001\\
Work-Public&  5.00 & <0.0253 & 5,129	& 0.001\\
\hline
\end{tabular}
\caption{Results of a chi-square test to examine VUR based on data recipient, across all data points.}
\label{recipient-chi}
\end{center}
\end{table}
